Hybrid oddball - SSVEP BCI

### 2013-04-22 draftHybridPaper/draftHybridBCI.tex
just a commit

\acrodef{SSVEP}{Steady-State Visually Evoked Potential}
\acrodef{BCI}{Brain-Computer Interface}

@@

    \subsection{Experiment 1: studying the oddball ERPs}
    \label{sec:2.2Oddball}

@@

        % Aim and subjects
        The aim of this first experiment was to study the effect of a flickering background on the typical ERP response associated to an oddball paradigm.
        N subjects participated in the experiment (age, gender).

@@

        As we aimed here at studying the effect of the flickering background on the oddball ERP response, we defined 5~experimental conditions.
        The first one (baseline) consisted of a run as described in the previous paragraph but in which no flickering background was displayed.
        The 4~other conditions differed only by the frequency of the flickering background; the frequencies used were \SIlist[list-units = single]{8.57;10;12;15}{\Hz}, corresponding to the division of the refreshing rate of the screen by \numlist{7;6;5;4}, respectively.

@@

        % use
        The data collected were used to compare the shape of the oddball response (response to the flashing of the target icon) and the ERP classification accuracy (response to target \emph{v.s.} response to non-target flasing) across conditions.

        \subsubsection{Data Analysis: ERP responses}
        \label{sec:2.2.2AnalysisErpShape}

@@

        \subsubsection{Data Analysis: ERP classification}
        \label{sec:2.2.3AnalysisErpClassification}

        % studying classification accuracy: no epoch rejection

@@

    \subsection{Experiment 1: studying the oddball ERPs}
    \label{sec:2.2Oddball}

    \subsection{Experiment 2: studying the \ac{SSVEP} responses}
    \label{sec:2.3SSVEP}

>>>>

\acrodef{SSVEP}{Steady-State Visually Evoked Potential}
\acrodef{BCI}{Brain-Computer Interface}
\acrodef{ERP}{Event Related Potential}
\acrodef{SVM}{Support Vector Machine}

@@

    \subsection{Experiment 1: studying the oddball \acsp{ERP}}
    \label{sec:2.2Oddball}

@@

        % Aim and subjects
        The aim of this first experiment was to study the effect of a flickering background on the typical \ac{ERP} response associated to an oddball paradigm.
        N subjects participated in the experiment (age, gender).

@@

        As we aimed here at studying the effect of the flickering background on the oddball \ac{ERP} response, we considered 5~experimental conditions.
        The first one (baseline) consisted of a run as described in the previous paragraph but in which no flickering background was displayed.
        The 4~other conditions differed only by the frequency of the flickering background; the frequencies used were \SIlist[list-units = single]{8.57;10;12;15}{\Hz}, corresponding to the division of the refreshing rate of the screen by \numlist{7;6;5;4}, respectively.

@@

        % use
        The data collected were used to compare the shape of the oddball response (response to the flashing of the target icon) and the \ac{ERP} classification accuracy (response to target \emph{v.s.} response to non-target flasing) across conditions.

        \subsubsection{Data Analysis: \acs{ERP} responses}
        \label{sec:2.2.2AnalysisErpShape}

@@

        \subsubsection{Data Analysis: \acs{ERP} classification}
        \label{sec:2.2.3AnalysisErpClassification}

        % studying classification accuracy: no epoch rejection
        We are also interested in studying the effect of the flickering stimulus on the target \ac{ERP} detection accuracy.
        As the accuracy of an oddball \ac{BCI} is known to depend on the number of repetitions of flashing sequences used to average the \acp{ERP}; the classification accuracy was measured on \acp{ERP} averaged over the $n$~first repetitions of the flashing sequence with $n$~going from 1~to~10.
        This was done so as to mimic a real use of the system (where the stimulation sequence would stop after $n$~repetitions) and so that the accuracies are always measured on the same number of detection attempts.

        For each experimental condition

        Data were filtered between \SIlist[list-units = single]{0.3;15}{\Hz} (zero-phase 3\rd order Butterworth filter), cut into \SI{800}{\ms} epochs starting from the stimuli onsets and downsampled to \SI{128}{\Hz}.

        For each trial (stimulus), we had 8~channels~$\times$~80~data~points~=~640~features to classify as a response to either a target stimulus or a non-target stimulus.
        A linear \emph{Support Vector Machine} (SVM; \cite{Cristianini2000,Suykens2002}) with a 10-fold cross-validation and a linesearch for the optimization of the regularization parameter was built from the normalized training features.
        Training the linear SVM with the modified finite Newton method proposed by \textcite{Keerthi2006} took around one minute.

@@

    \subsection{Experiment 1: studying the oddball \acsp{ERP}}
    \label{sec:2.2Oddball}
